\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-20 paper.qmd
Add benchmark value to remove long edges tunning section

```{r}
#| echo: false
#| warning: false
#| fig-cap: Goodness of fit statistics from different NLDR techniques applied to training S-curve dataset with different benchmark values to remove the low-density heaxgons. What is the effective benchmark value to remove the low-density heaxgons?
#| label: fig-diagnosticpltScurvelwd
#| out-width: 100%

aic_plot_lwd + mse_plot_lwd +
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides='collect', ncol = 2) &
  theme(legend.position='bottom', plot.tag = element_text(size = 8))
```

@@

@@

```{r}
#| echo: false
#| warning: false
#| fig-cap: Goodness of fit statistics from different NLDR techniques applied to training S-curve dataset with different benchmark values to remove the long edges. What is the effective benchmark value to remove the long edges?
#| label: fig-diagnosticpltScurvelgrm
#| out-width: 100%

aic_plot_lg + mse_plot_lg +
  plot_annotation(tag_levels = 'a') +
  plot_layout(guides='collect', ncol = 2) &
  theme(legend.position='bottom', plot.tag = element_text(size = 8)) 
```

>>>>

```{r}
#| echo: false
#| warning: false
#| fig-cap: Goodness of fit statistics from different NLDR techniques applied to training S-curve dataset with different benchmark values to remove the low-density heaxgons. What is the effective benchmark value to remove the low-density heaxgons?
#| label: fig-diagnosticpltScurvelwd
##| out-width: 100%

#aic_plot_lwd + 
  mse_plot_lwd +
  #plot_annotation(tag_levels = 'a') +
  plot_layout(guides='collect', ncol = 2) &
  theme(legend.position='bottom', plot.tag = element_text(size = 8))
```

@@

Achieving a smooth representation in 2D space is crucial, and one factor influencing this smoothness is the presence of long edges. These long edges occur when a line connects points that are distant in the triangular mesh, impacting the overall smoothness of the mesh.

To investigate the effect of removing long edges on the MSE, we analyzed the MSE for various benchmark values. Surprisingly, the results indicated that the MSE remained consistent across different benchmark values, as shown in @fig-diagnosticpltScurvelgrm. It's important to note that edges are defined only in the 2D model and do not extend to higher dimensions. Consequently, removing edges does not affect the model in higher dimensions.

There is no definitive rule for determining the benchmark value to remove long edges. However, we have a method to find a default value (see Appendix). Adjusting values around this default can help to find benchmark value to remove long edges, contributing to the construction of a smoother 2D representation.

@@

```{r}
#| echo: false
#| warning: false
#| fig-cap: Goodness of fit statistics from different NLDR techniques applied to training S-curve dataset with different benchmark values to remove the long edges. What is the effective benchmark value to remove the long edges?
#| label: fig-diagnosticpltScurvelgrm
##| out-width: 100%

#aic_plot_lg + 
  mse_plot_lg +
  #plot_annotation(tag_levels = 'a') +
  plot_layout(guides='collect', ncol = 2) &
  theme(legend.position='bottom', plot.tag = element_text(size = 8)) 
```

### 2024-01-20 paper.tex
Add benchmark value to remove long edges tunning section

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, breakable]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-diagnosticpltScurvelwd-1.pdf}

@@

@@

{\centering \includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-diagnosticpltScurvelgrm-1.pdf}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, sharp corners, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, breakable]}{\end{tcolorbox}}\fi

@@

{\centering \includegraphics{paper_files/figure-pdf/fig-diagnosticpltScurvelwd-1.pdf}

@@

Achieving a smooth representation in 2D space is crucial, and one factor
influencing this smoothness is the presence of long edges. These long
edges occur when a line connects points that are distant in the
triangular mesh, impacting the overall smoothness of the mesh.

To investigate the effect of removing long edges on the MSE, we analyzed
the MSE for various benchmark values. Surprisingly, the results
indicated that the MSE remained consistent across different benchmark
values, as shown in Figure~\ref{fig-diagnosticpltScurvelgrm}. It's
important to note that edges are defined only in the 2D model and do not
extend to higher dimensions. Consequently, removing edges does not
affect the model in higher dimensions.

There is no definitive rule for determining the benchmark value to
remove long edges. However, we have a method to find a default value
(see Appendix). Adjusting values around this default can help to find
benchmark value to remove long edges, contributing to the construction
of a smoother 2D representation.

@@

{\centering \includegraphics{paper_files/figure-pdf/fig-diagnosticpltScurvelgrm-1.pdf}
